---
title: "PS270 Final Project"
author: Ella Gorodetzky
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Introduction

Is there a correlation between attacks on journalists and location? In this study, I will use the U.S. Press Freedom Tracker's Incidents Database (https://pressfreedomtracker.us/all-incidents/?endpage=3) to measure if the likelihood of an attack targeted at a journalist correlates to location in the United States, looking specifically at region and state. I hypothesize that some states have more incidents than others. The first variable I will use is attacks on journalists in the U.S. The next variable I will use is states. The variable I will create is region, using the states variable. The outcome variable I will measure is which states or regions in the U.S. have the most attacks on journalists. The observed pattern will be correlation between U.S. location and attacks on journalists.


## Data


```{r}
library(tidyverse)
library(infer)
incidents <- read_csv("~/incidents.csv")
incidents
```

```{r}
incidents_region <- incidents |>
  mutate(region = case_when(state == "Washington (WA)" ~ 0,
                            state == "Oregon (OR)" ~ 0,
                            state == "California (CA)" ~ 0,
                            state == "Idaho (ID)" ~ 0,
                            state == "Nevada (NV)" ~ 0,
                            state == "Montana (MT)" ~ 0,
                            state == "Wyoming (WY)" ~ 0,
                            state == "Utah (UT)" ~ 0,
                            state == "Colorado (CO)" ~ 0,
                            state == "Alaska (AK)" ~ 0,
                            state == "Hawaii (HI)" ~ 0,
                            state == "Arizona (AZ)" ~ 1,
                            state == "New Mexico (NM)" ~ 1,
                            state == "Texas (TX)" ~ 1,
                            state == "Oklahoma (OK)" ~ 1,
                            state == "North Dakota (ND)" ~ 2,
                            state == "South Dakota (SD)" ~ 2,
                            state == "Nebraska (NB)" ~ 2,
                            state == "Kansas (KS)" ~ 2,
                            state == "Minnesota (MN)" ~ 2,
                            state == "Iowa (IA)" ~ 2,
                            state == "Missouri (MO)" ~ 2,
                            state == "Wisconsin (WI)" ~ 2,
                            state == "Illinois (IL)" ~ 2,
                            state == "Michigan (MI)" ~ 2,
                            state == "Indiana (IN)" ~ 2,
                            state == "Ohio (OH)" ~ 2,
                            state == "Nebraska (NE)" ~ 2,
                            state == "Arkansas (AR)" ~ 3,
                            state == "Louisiana (LA)" ~ 3,
                            state == "Mississippi (MS)" ~ 3,
                            state == "Alabama (AL)" ~ 3,
                            state == "Kentucky (KY)" ~ 3,
                            state == "Tennessee (TN)" ~ 3,
                            state == "Georgia (GA)" ~ 3,
                            state == "Florida (FL)" ~ 3,
                            state == "West Virginia (WV)" ~ 3,
                            state == "Virginia (VA)" ~ 3,
                            state == "North Carolina (NC)" ~ 3,
                            state == "South Carolina (SC)" ~ 3,
                            state == "Maine (ME)" ~ 4,
                            state == "Vermont (VT)" ~ 4,
                            state == "New Hampshire (NH)" ~ 4,
                            state == "Massachusetts (MA)" ~ 4,
                            state == "Connecticut (CT)" ~ 4,
                            state == "Rhode Island (RI)" ~ 4,
                            state == "New York (NY)" ~ 4,
                            state == "New Jersey (NJ)" ~ 4,
                            state == "Pennsylvania (PA)" ~ 4,
                            state == "Maryland (MD)" ~ 4,
                            state == "Delaware (DE)" ~ 4,
                            state == "District of Columbia (DC)" ~ 4,
                            state == "Puerto Rico (PR)" ~ 5,
                            state == "None" ~ 5)) |>
  mutate(Region = case_when(region == 0 ~ "West",
                            region == 1 ~ "Southwest",
                            region == 2 ~ "Midwest",
                            region == 3 ~ "Southeast",
                            region == 4 ~ "Northeast",
                            region == 5 ~ "other")) |>
  mutate(journalist_targeted_number = case_when(was_journalist_targeted == "no" ~ 0,
                                                was_journalist_targeted == "None" ~ 0,
                                                was_journalist_targeted == "unknown" ~ 1,
                                                was_journalist_targeted == "yes" ~ 2)) |>
  mutate(journalist_targeted_yes_no = if_else(was_journalist_targeted == "yes", "Targeted", "Not Targeted"))
incidents_region
```

```{r}
incidents_plot_region <- incidents_region |>
  group_by(journalist_targeted_number) |>
  summarize(Region, na.rm = TRUE) |>
  ggplot(aes(x = Region, y = journalist_targeted_number)) +
  geom_col() +
  labs(x = "U.S. Region", y = "Was Journalist Targeted", title = "Incidents of U.S. Journalists Targeted By Region")
incidents_plot_region
```


```{r}
incidents_plot_state <- incidents |>
  group_by(state, was_journalist_targeted) |>
  summarize(mean(state, na.rm = TRUE)) |>
  ggplot(aes(x = was_journalist_targeted, y = state)) +
  geom_boxplot() +
  labs(x = "Was Journalist Targeted", y = "U.S. State", title = "Incidents of U.S. Journalists Targeted By State")
incidents_plot_state
```


## Results

```{r}
incidents_table_state <- incidents_region |>
  group_by(was_journalist_targeted) |>
  reframe(state) |>
  filter(was_journalist_targeted == "yes")
incidents_table_state

knitr::kable(incidents_table_state, col.names = c("Was Journalist Targeted", "U.S. State"))
```
California, District of Columbia, Florida, Illinois, Michigan, Minnesota, New York, and Oregon were some of the states that had a larger number of incidents where journalists were targeted. I can hypothesize that this is because these states all contain big cities.

```{r}
incidents_table_region <- incidents_region |>
  group_by(was_journalist_targeted) |>
  reframe(Region) |>
  filter(was_journalist_targeted == "yes")
incidents_table_region

knitr::kable(incidents_table_region, col.names = c("Was Journalist Targeted", "U.S. Region"))
```

The region West has the most incidents of attacks targeted at journalists. I can hypothesize that this is because this region includes both California and Oregon, which had two of the highest number of targeted attacks on journalists according to the previous table. The next highest was Northeast, which I can hypothesize is because it includes District of Columbia and New York.

```{r}
lm(journalist_targeted_number ~ Region, data = incidents_region)
```
The region West has a coefficient of 1.190e+00, which is the highest of all the regions. This is significant because the West had the highest number of targeted attacks on journalists, meaning we can interpret the data causally.

## Conclusion

My hypothesis was that there would be a correlation between location and targeted attacks on journalist across the U.S. After interpreting the data, I can conclude that there is a correlation. The graphs and tables show that the West region had the most incidents of attacks targeted against journalist, as well as state with big cities. I can conclude that there is a correlation, however, this cannot be interpreted causally because it does not factor in other variables, such as if protests occurred around the time of the incidents, or if other significant events happened that may have given another reason for the targeted attacks.




