---
title: "PS270 Final Project"
author: Ella Gorodetzky
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

Do most attacks targeted at journalists occur around protests? In this study, I will use the U.S. Press Freedom Tracker's Incidents Database (https://pressfreedomtracker.us/all-incidents/?endpage=3) to measure if the occurrence of a protest effects the likelihood of an attack targeted at a journalist. I hypothesize that protesting does spark journalist attacks. The first variable I will use is attacks on journalists in the U.S. The next variable I will use is protests in the U.S. that turn violent. The outcome variable I will measure if how many of those protests include attacks on journalists. The observed pattern will be correlation between violence at protests and journalists.


```{r}
library(tidyverse)
```

```{r}
incidents <- read_csv("~/incidents.csv")
incidents
```


```{r}
incidents_plot <- incidents |>
  group_by(categories, was_journalist_targeted) |>
  ggplot(aes(x = was_journalist_targeted, y = categories)) +
  geom_col()
incidents_plot
```


