---
title: "PS270 Final Project"
author: Ella Gorodetzky
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

Is there a correlation between attacks on U.S. jouranlists and location? In this study, I will use the U.S. Press Freedom Tracker's Incidents Database (https://pressfreedomtracker.us/all-incidents/?endpage=3) to measure if the occurrence of a protest effects the likelihood of an attack targeted at a journalist. I hypothesize that some states have more incidents than others. The first variable I will use is attacks on journalists in the U.S. The next variable I will use is states. The outcome variable I will measure is which states in the U.S. have the most attacks on journalists, and if this correlates to dominant ideologies in those states. The observed pattern will be correlation between states and attacks on journalists.


```{r}
library(tidyverse)
```

```{r}
incidents <- read_csv("~/incidents.csv")
incidents
```
cces |>
mutate(educ_ordinal = case_when(educ=="No HS" ~ 0,
educ=="High school graduate" ~ 1,
educ=="Some college" ~ 2,
educ=="2-year" ~ 3,
educ=="4-year" ~ 4,
educ=="Post-grad" ~ 5,)) |>
select(educ, educ_ordinal)
```{r}
incidents_region <- incidents |>
  mutate(region = case_when(state == "Washington (WA)" ~ 0,
                            state == "Oregon (OR)" ~ 0,
                            state == "California (CA)" ~ 0,
                            state == "Idaho (ID)" ~ 0,
                            state == "Nevada (NV)" ~ 0,
                            state == "Montana (MT)" ~ 0,
                            state == "Wyoming (WY)" ~ 0,
                            state == "Utah (UT)" ~ 0,
                            state == "Colorado (CO)" ~ 0,
                            state == "Arizona (AZ)" ~ 1,
                            state == "New Mexico(NM)" ~ 1,
                            state == "Texas (TX)" ~ 1,
                            state == "Oklahoma (OK)" ~ 1,
                            state == "North Dakota (ND)" ~ 2,
                            state == "South Dakota (SD)" ~ 2,
                            state == "Nebraska (NB)" ~ 2,
                            state == "Kansas (KS)" ~ 2,
                            state == "Minnesota (MN)" ~ 2,
                            state == "Iowa (IA)" ~ 2,
                            state == "Missouri (MO)" ~ 2,
                            state == "Wisconsin (WI)" ~ 2,
                            state == "Illinois (IL)" ~ 2,
                            state == "Michigan (MI)" ~ 2,
                            state == "Indiana (IN)" ~ 2,
                            state == "Ohio (OH)" ~ 2,
                            state == "Arkansas (AR)" ~ 3,
                            state == "Louisiana (LA)" ~ 3,
                            state == "Mississippi (MS)" ~ 3,
                            state == "Alabama (AL)" ~ 3,
                            state == "Kentucky (KY)" ~ 3,
                            state == "Tennesee (TN)" ~ 3,
                            state == "Georgia (GA)" ~ 3,
                            state == "Florida (FL)" ~ 3,
                            state == "West Virginia (WV)" ~ 3,
                            state == "Virginia (VA)" ~ 3,
                            state == "North Carolina (NC)" ~ 3,
                            state == "South Carolina (SC)" ~ 3,
                            state == "Maine (ME)" ~ 4,
                            state == "Vermont (VT)" ~ 4,
                            state == "New Hampshire (NH)" ~ 4,
                            state == "Massachusetts (MA)" ~ 4,
                            state == "Connecticut (CT)" ~ 4,
                            state == "Rhode Island (RI)" ~ 4,
                            state == "New York (NY)" ~ 4,
                            state == "New Jersey (NJ)" ~ 4,
                            state == "Pennsylvania (PA)" ~ 4,
                            state == "Maryland (MD)" ~ 4,
                            state == "Delaware (DE)" ~ 4))
incidents_region
```
```{r}
incidents_plot <- incidents_region |>
  group_by(was_journalist_targeted) |>
  summarize(region) |>
  ggplot(aes(x = was_journalist_targeted, y = region)) +
  geom_col() +
  labs(x = "Was Journalist Targeted", y = "U.S. Region", title = "Incidents of U.S. Journalists Targeted By State")
incidents_plot
```



```{r}
incidents_plot <- incidents |>
  group_by(state, was_journalist_targeted) |>
  summarize(mean(state, na.rm = TRUE)) |>
  ggplot(aes(x = was_journalist_targeted, y = state)) +
  geom_boxplot() +
  labs(x = "Was Journalist Targeted", y = "State", title = "Incidents of U.S. Journalists Targeted By State")
incidents_plot
```

California, District of Columbia, Florida, Illinois, Michigan, Minnesota, New York, and Oregon were some of the states that had a larger number of incidents where journalists were targeted. I can hypothesize that this is because these states all contain big cities.

```{r}
incidents_table <- incidents |>
  group_by(was_journalist_targeted, state) |>
  summarize(was_journalist_targeted, state)
incidents_table

knitr::kable(incidents_table)
```
